text mining

### 2017-07-07 cheatsheets/textmining_cheatsheet.Rmd
added notes

#finds the 10 most frequent terms (doesn't mattern what kind of word, all words treated equally)
term_count <- freq_terms(new_text, 10)
plot(term_count)
```

### tm package and creating volatile corpus
* to make a volatile corpus, need to have R interpret each element in vector of text as a document, us tm package and its source functions to do this: VectorSource(), which outputs a source object
* example: coffee_source <- VectorSource(coffee_tweets) (to convert vector to a source object)
* then pass source to VCorpus(), which is a list of lists: at each element of the corpus, there is a plain text document, which is essentially a list that contains the actual text data (since it's a list of lists, need to subset twice to get to the actual text data)
* use DataframeSource() when making corpus from dataframe: treats entire row as a complete document (careful not to pick up non-text data)
```{r}
num  <- c(1,2,3)
Author1 <- c("Text mining is a great time.", "Text analysis provides insights", "qdap and tm are used in text mining")
Author2 <- c("R is a great language", "R has many uses", "DataCamp is cool!")
example_text <- cbind(num, Author1, Author2)

@@

>>>>

#finds the 10 most frequent terms (doesn't mattern what kind of word, all words treated equally)
term_count <- freq_terms(text, 10)
plot(term_count)
```

### tm package and creating volatile corpus
* to make a volatile corpus, need to have R interpret each element in vector of text as a document, us tm package and its source functions to do this: VectorSource(), which outputs a source object
* example: coffee_source <- VectorSource(coffee_tweets) (to convert vector to a source object)
* then pass source to VCorpus(), which is a list of lists: at each element of the corpus, there is a plain text document, which is essentially a list that contains the actual text data (since it's a list of lists, need to subset twice to get to the actual text data)
* use DataframeSource() when making corpus from dataframe: treats entire row as a complete document (careful not to pick up non-text data)
```{r}
library(tm)
num  <- c(1,2,3)
Author1 <- c("Text mining is a great time.", "Text analysis provides insights", "qdap and tm are used in text mining")
Author2 <- c("R is a great language", "R has many uses", "DataCamp is cool!")
example_text <- cbind(num, Author1, Author2)

@@

### Visualizing common words (process for visualizing dissimilar words is similar to this)
* visualize common words across multiple documents: commonality_cloud()
* use paste function and collapse = " " to create a vector containing all documents
* use VectorSource() to convert vector to vector source
* use VCorpus() on the vector source to create corpus 
* then clean corpus, convert it to TDM, convert it to matrix, then use commonality.cloud() with max.words and colors arguments

### other visualizations 
* create word networks with word_associate() function
* can create dendrograms 
* word associations: findAssocs(tdm, "word", 0.25), returns a list, for any given word, calculates its correlation with every other word in a TDM or DTM

### term frequency-inverse document frequency
* if a term appears frequently it must be important, but if it appears in all documents- not likely to be important:
* TfIdf score increases by term occurrence but is penalized by the frequency of appearance among all documents
* use: control = list(weighting = weightTfIdf) in TermDocumentMatrix function
